---
title: "607_assignment_3"
output: html_document
date: "2023-02-09"
---

```{r}
library(tidyverse)
library(dbplyr)
library(stringr)
library(stringi)

```

## Exercise 1
Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset, [link](https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/) provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r}
##read csv and see the header
readfile <- data.frame(read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv", header = TRUE))

head(readfile)

## search for majors contains DATA or STATISTICS
data_stat_df <-grep("DATA|STATISTICS", readfile$Major, value = TRUE)

head(data_stat_df)

```

## Exercise 2
Write code that transforms the data below:
[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"
Into a format like this:
c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r}
##input the data to a dataframe

new_df <- {
'
[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"
'
}
new_df
##remove the unknown characters
new_df<-str_remove_all(new_df,"\"")
new_df<-str_remove_all(new_df,"\n")
new_df

##sort the string
sort(new_df)

new_list <-c(new_df)

new_list
```
## Exercise 3
Describe, in words, what these expressions will match:
*(.)\1\1
This expression returns value with characters repeated 3 times.
```{r}
test_word <- c("goddesssship", "juice", "skullllike", "skull", "hostesssship")
str_subset(test_word, "(.)\\1\\1")

```

*(.)(.)\\2\\1
This expression returns value with pairs characters.
```{r}
test_word2 <- c("abba", "music", "fruits", "candy", "choco")
str_subset(test_word2, "(.)(.)\\2\\1")
```
*(..)\1
This expression returns value with any characters repeated.
```{r}
test_word3 <-c("banana","sausage", "music", "silver", "muscle")
str_subset(test_word3, "(..)\\1")
```
*(.).\\1.\\1
This expression returns characters that have other characters in between 2 original characters.
```{r}
test_word4 <- c("banana", "Alabama", "sushi", "sugar", "bowl")
str_subset(test_word4, "(.).\\1.\\1")
```
*(.)(.)(.).*\\3\\2\\1
This expression returns characters that have others characters in between 2 character sets in reversed order.
```{r}
test_word5 <- c("xyz1zyx", "doggod", "sworddrows", "music", "mussle")
str_subset(test_word5, "(.)(.)(.).*\\3\\2\\1")
```

## Exercise 4
Construct regular expressions to match words that:
Start and end with the same character.

```{r}
test_word6 <- c("dad", "music", "razor", "banana", "burritos")
str_subset(test_word6, "^(.)((.*\\1$)|\\1?$)")
```
Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r}
test_word7 <- c("church", "monster", "banana", "jujube", "star")
str_subset(test_word7, "([A-Za-z][A-Za-z]).*\\1")
```
Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
```{r}
test_word8 <- c("eleven", "balloon", "expression", "repeat", "banana")
str_subset(test_word8, "([a-z]).*\\1.*\\1")
```